Forecasting U.S. Presidential Election Outcomes: A Poll-Based Predictive Model Using YouGov Data

### 2024-11-03 paper/paper.qmd
Add citation.

---
title: "Forecasting U.S. Presidential Election Outcomes: A Poll-Based Predictive Model Using YouGov Data"
subtitle: "Analyzing the Impact of Political Party, Candidate Name, and Sample Size on Vote Share Predictions"
author: 
  - Yizhe Chen
  - Charlie Zhang
  - Qizhou Xie
thanks: "Code and data are available at: [https://github.com/YizheChenUT/Election_Forecasting_Model.git](https://github.com/YizheChenUT/Election_Forecasting_Model.git)."
date: today
date-format: long
abstract: "This paper presents a linear regression model that predicts the percentage of votes for presidential candidates based on polling data from YouGov. The model incorporates key predictors such as political party, candidate name, sample size, and polling end date. Our results show that both political party affiliation and sample size significantly affect the predicted vote share, with Republican candidates often receiving higher predicted percentages. This study highlights the importance of integrating candidate-specific and poll-specific factors to improve election forecasts, providing useful insights for political analysts and pollsters."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(tidyverse)
```

# Introduction

Polling data plays a critical role in shaping public opinion and forecasting election outcomes, particularly in democratic societies where political campaigns rely heavily on polls to gauge voter preferences. In the context of the U.S. presidential elections, the accuracy of poll-based predictions has become increasingly important for political parties, candidates, and media organizations. Despite the growing reliance on polling, there are several challenges in making accurate predictions, such as sample selection, timing of the poll, and candidate-specific factors.

This paper aims to build a predictive model using polling data from YouGov, one of the most recognized polling agencies, to forecast the percentage of votes for presidential candidates. The model incorporates variables such as political party, candidate name, sample size, and the poll's end date. By focusing on a single pollster, this study seeks to analyze the effect of these factors on vote share predictions and contribute to the broader literature on election forecasting.

The estimand of the model is the predicted percentage of votes that each candidate is expected to receive, which is influenced by the selected variables. Our findings suggest that both the political party of a candidate and the sample size of the poll significantly affect vote share predictions. These results are important as they provide valuable insights into how different factors influence the accuracy of polling predictions, potentially improving the quality of future election forecasts.

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR] to process and analyze the polling data sourced from YouGov, one of the leading polling agencies for U.S. elections. The dataset includes several key variables that are important for predicting the percentage of votes each presidential candidate might receive, such as candidate name, political party, sample size, and the polling end date. Following the approach outlined by @tellingstories, we incorporate both candidate-specific and poll-specific factors to improve the accuracy of our model.

The data was cleaned and processed to ensure that all missing values for the vote percentage (pct) were removed, and categorical variables like candidate name and political party were properly encoded. Additionally, sample sizes and dates were standardized for consistency across all polling entries.

## Measurement

Polling data, in essence, represents a snapshot of public opinion at a given time. In our case, the dataset captures public opinion on various presidential candidates based on responses collected via YouGov's online surveys. These responses are translated into numerical entries in the dataset, such as the predicted percentage of votes a candidate might receive (pct), the number of respondents (sample_size), and the poll's end date (end_date).

## Outcome variables

The primary outcome variable in our dataset is the predicted percentage of votes (pct) for each candidate. This variable is influenced by several factors, including the candidate's political party, the sample size of the poll, and the timing of the poll. To illustrate the distribution of vote percentages for candidates from different political parties, we present the following graph.

@@

## Sample size

Another important aspect of our data is the sample size, which varies between polls. Larger sample sizes tend to produce more reliable predictions, as they better capture the diversity of voter preferences. Below, we show the relationship between sample size and predicted vote share.

@@

In @fig-sample-size, we observe that larger sample sizes tend to produce a wider range of vote percentages. This suggests that larger polls may capture more nuanced variations in voter preferences, which could be critical in tight election races.

## Predictor variables

Several predictor variables were included in our model to estimate the percentage of votes for each candidate. These variables include:

@@

# Model

The goal of our modeling strategy is twofold. Firstly, we aim to predict the percentage of votes each presidential candidate will receive using polling data from YouGov. Secondly, we seek to understand how key factors—such as political party, candidate name, sample size, and polling end date—affect vote share predictions.

@@

## Model set-up

Define $y_i$ as the predicted percentage of votes for candidate $i$, and $\texttt{party}_i$, $\texttt{candidate}_i$, $\texttt{sample\_size}_i$, and $\texttt{end\_date}_i$ as the political party, candidate name, sample size, and polling end date for candidate $i$ respectively.

@@

$y_i | \mu_i, \sigma \sim \text{Normal}(\mu_i, \sigma)$

@@

$\mu_i = \alpha + \beta_1 \cdot \texttt{party}_i + \beta_2 \cdot \texttt{candidate}_i + \beta_3 \cdot \texttt{sample\_size}_i + \beta_4 \cdot \texttt{end\_date}_i$

@@

$\alpha \sim \text{Normal}(0, 2.5)$
$\beta_1, \beta_2, \beta_3, \beta_4 \sim \text{Normal}(0, 2.5)$
$\sigma \sim \text{Exponential}(1)$

@@

## Model justification

We expect a significant relationship between the predictors and the percentage of votes. Specifically, political party is expected to have a substantial impact, as previous polls suggest that party affiliation strongly correlates with voter preferences. Additionally, sample size is an important predictor, as larger sample sizes tend to provide more reliable estimates. Polls conducted closer to the election (end date) may also capture more accurate voter sentiments, leading to better predictions.

@@

# Results

Our results are summarized in @tbl-modelresults. The model was designed to predict the percentage of votes each presidential candidate might receive based on several key factors: political party, candidate name, sample size, and polling end date. Below, we present a table of the model's coefficients, followed by visualizations of the relationship between the predictors and the predicted vote share.

@@

library(rstanarm)

@@

modelsummary::modelsummary(
  list(
    "Vote Share Prediction Model" = first_model
  ),
  statistic = "mad",  # Mean absolute deviation
  fmt = 2  # Format to 2 decimal places
)
```

@@

## Key Findings

- Political Party: The results show that the Republican party has a small positive effect on vote share predictions, while third-party candidates generally have lower predicted percentages.

@@

## Visualization of Results

We now turn to graphical representations to illustrate the relationship between sample size and predicted vote percentage, as well as the effect of political party on the predicted vote share.

@@

# Discussion

## Overview of Findings

In this paper, we built a predictive model to estimate the vote share of U.S. presidential candidates using polling data, with key predictors including political party, candidate name, sample size, and polling end date. The goal was to understand how these factors influence predicted vote shares, and to gain insights into the dynamics of political polling. The model’s high $R^2$ value (0.964) indicates it explains a substantial amount of variation in vote predictions, suggesting that it successfully captures relevant trends in the data. This outcome offers a deeper understanding of the factors driving poll-based vote share predictions in U.S. elections.

## Insights into Political Influence on Vote Share

One key finding from this analysis is the impact of political party on vote share predictions. Our model indicates that candidates from major parties, particularly Republicans, tend to receive higher predicted vote shares compared to third-party candidates. This is consistent with historical trends, where major-party candidates generally dominate U.S. elections. The model reinforces the idea that party affiliation is a powerful determinant in voter preferences, reflecting the established influence of major parties in American politics. This insight aligns with broader theories in political science, where party affiliation often serves as a shortcut for voters, helping them make quick decisions about candidates based on their general political orientation.

## Candidate-Specific Effects on Vote Share

Another important takeaway is the effect of candidate-specific factors on vote share predictions. Certain candidates, such as Joe Biden and Kamala Harris, show positive coefficients, indicating they are expected to receive a higher share of votes compared to others like Mike Pence or Vivek Ramaswamy. This suggests that individual characteristics and name recognition may play a role in influencing voter support. Recognizable figures with established reputations, such as former presidents or vice presidents, may have an advantage in polls due to higher visibility and public familiarity. This finding highlights the importance of candidate characteristics beyond party affiliation and points to the potential value of including more candidate-specific variables, such as favorability ratings, in future models.

## Limitations of Sample Size and Polling End Date as Predictors

Despite the high explanatory power of the model, certain predictors—particularly sample size and polling end date—show little to no effect on vote share predictions. This result might initially seem counterintuitive, as larger sample sizes are generally associated with higher reliability in survey research. However, in this case, the lack of impact could suggest that once a minimum sample threshold is met, the additional respondents do not significantly alter the predicted vote share. Similarly, the end date of the poll may have little impact because public opinion might not shift drastically over short periods, especially if polling occurs well before the election. This raises questions about the utility of these predictors in vote share models and suggests that additional contextual factors, such as the timing of major political events, could be more meaningful.

## Weaknesses and Next Steps

While this model provides valuable insights, it also has some limitations. First, the model does not incorporate a variable for state-level differences, which could be significant in the U.S. electoral system, where the Electoral College, not the popular vote, ultimately determines the election outcome. A more detailed model could include state as a predictor or even focus on state-level vote shares to estimate Electoral College outcomes.

@@

## Concluding Remarks and Future Directions

This analysis contributes to our understanding of how polling data can be used to predict election outcomes, highlighting the importance of political party and candidate characteristics in influencing vote shares. However, there remains much to explore. Future research could expand on this model by integrating additional predictors, such as candidate favorability and recent political events, or by building state-level models to predict Electoral College outcomes.

@@

# Appendix {-}

# Detailed Analysis of YouGov's Polling Methodology

## Overview of YouGov's Polling Approach

YouGov is a prominent polling agency known for its methodological rigor and unique approach to online surveys. This appendix delves into YouGov's methodology, examining its sample selection, recruitment techniques, and the reliability and limitations inherent in its survey process.

## Population, Frame, and Sample

The population targeted by YouGov’s polls comprises U.S. adult citizens, providing a frame that includes diverse demographics such as age, gender, race, income level, and political affiliation. The samples are drawn from an online panel of respondents who voluntarily participate in YouGov’s surveys. By leveraging an extensive online panel, YouGov strives to capture a broad, representative slice of public opinion on various political issues, including presidential election intent, candidate favorability, and policy priorities.

## Sampling and Recruitment

YouGov employs a non-probability sampling approach, specifically targeting individuals within its online panel. While this method allows YouGov to reach a large and diverse set of respondents quickly, it introduces certain limitations in terms of randomization and representativeness compared to traditional random sampling methods. To mitigate these issues, YouGov uses sophisticated weighting techniques to adjust for demographic discrepancies, ensuring that the sample more accurately reflects the broader U.S. population.

## Sampling Approach: Trade-offs

The online nature of YouGov’s panel sampling allows for rapid and frequent polling. However, it also comes with trade-offs, particularly concerning coverage bias, as individuals without internet access or those less inclined to participate in online activities may be underrepresented. Additionally, while weighting adjustments improve representativeness, they cannot entirely compensate for the self-selection bias inherent in voluntary panel participation. This trade-off is a key factor to consider when interpreting results, as online samples may sometimes diverge from outcomes in broader, random-sample-based polls.

## Non-response Handling

To address potential non-response bias, YouGov employs weighting adjustments based on demographic factors such as age, gender, education, and political affiliation. By adjusting responses according to these factors, YouGov attempts to balance out any biases introduced by individuals who choose not to respond to specific questions or surveys entirely. This weighting process helps align the sample's characteristics with the intended population, although it does not completely eliminate non-response bias.

## Questionnaire Design

YouGov’s questionnaires are carefully crafted to gather specific insights into voters’ opinions on candidates, political parties, and policy issues. The questions are standardized to allow comparison over time, aiding trend analysis. However, the online format of the questionnaire could impact responses, as participants are aware they are not in a monitored, controlled setting. Despite this limitation, YouGov’s design ensures clarity and consistency, although some complex topics may benefit from further simplification to enhance understanding across diverse education levels.

## Strengths and Weaknesses

### Strengths

- Speed and Flexibility: The online sampling and recruitment model enables YouGov to conduct polls swiftly, which is particularly valuable in fast-moving political contexts.

@@

### Weaknesses

- Selection Bias: As participants self-select into the online panel, there is an inherent selection bias that even weighting cannot fully mitigate.

@@

# Idealized Methodology and Survey for Forecasting the U.S. Presidential Election

This appendix provides a detailed methodology for conducting an election forecasting survey with a $100,000 budget. The methodology focuses on achieving representativeness, accuracy, and data quality. The survey includes stratified sampling, multi-channel recruitment, data validation, and careful questionnaire design, implemented via Google Forms.

## Methodology Overview

This survey aims to forecast U.S. presidential election outcomes by capturing voting intentions and priorities across various demographic groups. With a $100,000 budget, we estimate reaching a sample size of approximately 5,000 respondents. This funding covers recruitment, incentives, and platform usage costs, ensuring a robust dataset that represents the U.S. voting population.

## Sampling Approach

Stratified Random Sampling will be employed, focusing on:
- Stratification Variables: Age, gender, race, income, education, and geography.
- Sample Size: With the $100K budget, the target sample size is approximately 5,000 respondents, based on cost estimates for recruitment, incentives, and platform usage.
- Random Selection: Participants will be randomly selected within each stratum to ensure demographic balance.

@@

## Recruitment Strategy

To reach a diverse population of respondents, the survey will use multi-channel recruitment, including:
- Social Media Advertising: Targeted ads on platforms such as Facebook, Twitter, and Instagram, directed toward U.S. users of various demographics.
- Email Outreach: Partnerships with organizations that can share the survey link with their networks.
- Incentives: Respondents will receive a small monetary incentive (e.g., $10 gift card) upon completing the survey, increasing participation rates while staying within budget.

@@

## Data Validation and Quality Control

To ensure data accuracy, several quality control measures will be in place:
- Screening Questions: Initial questions to confirm eligibility (e.g., age, U.S. citizenship).
- Attention Checks: Questions designed to ensure respondents are paying attention, helping filter out low-quality responses.
- Duplicate Responses: IP tracking and other technical measures to prevent duplicate submissions.
- Post-Survey Weighting: To correct for any imbalances in the sample, responses will be weighted based on demographic factors according to U.S. Census data, ensuring the final results better reflect the general population.

## Poll Aggregation and Reporting

This survey will be conducted in waves, with data collected at regular intervals leading up to the election. Results from each wave will be aggregated to provide a rolling average of voting intentions, smoothing out anomalies and highlighting trends. This approach will allow the survey to detect shifts in public opinion as the election approaches, providing a dynamic view of voter sentiment.

@@

## Survey Design

### Introductory Section

**Introduction**
Thank you for participating in our U.S. presidential election survey. Your responses will help us understand voting trends across the country. All responses are anonymous.
**Contact Information** 
For questions, contact us at yz.chen@mail.utoronto.ca

>>>>

---
title: "Forecasting U.S. Presidential Election Outcomes: A Poll-Based Predictive Model Using YouGov Data"
subtitle: "Analyzing the Impact of Political Party, Candidate Name, and Sample Size on Vote Share Predictions"
author: 
  - Yizhe Chen
  - Charlie Zhang
  - Qizhou Xie
thanks: "Code and data are available at: [https://github.com/YizheChenUT/Election_Forecasting_Model.git](https://github.com/YizheChenUT/Election_Forecasting_Model.git)."
date: today
date-format: long
abstract: "This study develops a Bayesian linear regression model to forecast U.S. presidential vote shares using polling data from YouGov, incorporating predictors like political party, candidate name, sample size, and poll end date. Key findings reveal that political party affiliation positively influences vote share, especially for major-party candidates, while candidate-specific characteristics, such as recognition, further impact predictions. Interestingly, sample size and polling end date show limited effects once minimum thresholds are met, suggesting stable voter sentiment over shorter periods and diminishing returns for larger samples. This model highlights the nuanced role of party and candidate factors in election forecasting and suggests directions for refining poll-based predictive models to enhance forecast accuracy."
format: pdf
pdf-engine: pdflatex
number-sections: true
toc: true
bibliography: references.bib
---

@@

library(tidyverse)
library(rstanarm)
library(modelsummary)
library(kableExtra)

# Introduction
Polling data is integral to shaping public opinion and predicting election outcomes, particularly within democratic societies where political campaigns rely on polls to understand and sway voter preferences. In the context of U.S. presidential elections, the precision of poll-based predictions holds increasing significance for political parties, candidates, and media organizations. However, accurately forecasting election outcomes involves multiple challenges, including the complexity of sample selection, timing, and candidate-specific factors.

This study builds a Bayesian linear regression model to forecast U.S. presidential vote shares using polling data from YouGov, a prominent polling agency. The model includes variables such as political party affiliation, candidate name, sample size, and the poll’s end date. By focusing on a single, high-quality data source, this research isolates the effects of these factors on vote share predictions, thereby contributing to the broader literature on election forecasting.

The primary estimand of this model is the predicted percentage of votes each candidate is expected to receive. The results show that political party affiliation plays a notable role in vote share predictions, with major-party candidates—particularly Republicans—generally receiving higher predicted shares. Additionally, candidate-specific factors like name recognition impact forecasts, while the effect of sample size and polling end date diminishes once a minimum threshold is reached. These findings underline the importance of incorporating both party and candidate characteristics into election models and suggest potential refinements for future poll-based forecasts.

The remainder of this paper is structured as follows: Section @sec-data provides an overview of the data, detailing its sources, cleaning procedures, and key variables like candidate name, political party, sample size, and polling end date. Section @sec-model discusses the model setup and justification, outlining the Bayesian linear regression approach and the rationale behind selecting specific predictors. Section @sec-result presents the results, examining the impact of party affiliation, candidate identity, and other factors on vote share predictions. Visualizations are included to illustrate key trends. Section @sec-disscussion explores broader implications, limitations, and potential extensions of this study, including sample size effects and directions for future research. Finally, sections @sec-appendix1 and @sec-appendix2 provide a detailed analysis of YouGov’s polling methodology and an idealized $100K survey methodology, offering practical insights for election forecasting.

# Data {#sec-data}
## Overview
We use the statistical programming language R [@citeR] to process and analyze the polling data sourced from YouGov [@YouGov], one of the leading polling agencies for U.S. elections. We use the httr package to download data [@httr] from the 538 website [@Wiederkehr]. The dataset includes several key variables that are important for predicting the percentage of votes each presidential candidate might receive, such as candidate name, political party, sample size, and the polling end date. Following the approach outlined by @tellingstories, we incorporate both candidate-specific and poll-specific factors to improve the accuracy of our model.

The data was cleaned and processed through the janitor package to ensure that all missing values for the vote percentage (pct) were removed, and categorical variables like candidate name and political party were properly encoded [@janitor]. Additionally, sample sizes and dates were standardized for consistency across all polling entries.

## Measurement
Polling data, in essence, represents a snapshot of public opinion at a given time. In our case, the dataset captures public opinion on various presidential candidates based on responses collected via YouGov's online surveys. These responses are translated into numerical entries in the dataset, such as the predicted percentage of votes a candidate might receive (pct), the number of respondents (sample_size), and the poll's end date (end_date).

## Outcome variables
The primary outcome variable in our dataset is the predicted percentage of votes (pct) for each candidate. This variable is influenced by several factors, including the candidate's political party, the sample size of the poll, and the timing of the poll. To illustrate the distribution of vote percentages for candidates from different political parties, we present the following graph.

@@

## Sample size
An essential aspect of our data is the sample size, which varies across polls. Generally, larger sample sizes improve prediction reliability by capturing a broader spectrum of voter preferences, thereby reducing variability in vote share estimates. However, our findings reveal that after reaching a certain sample threshold, additional respondents do not significantly impact predicted vote percentages.

@@

This result, illustrated in @fig-sample-size, indicates a limited relationship between sample size and vote share predictions, with smaller sample sizes yielding similarly accurate predictions beyond a minimal threshold.

Despite this, the data shows that larger sample sizes can still reveal a wider range of voter preferences. This observation suggests that while increased sample size may not substantially affect the accuracy of the predicted vote share, it could enhance the model's ability to capture nuanced variations in voter opinion, which is particularly valuable in closely contested races where small differences matter.

## Predictor variables
Several predictor variables were included in our model to estimate the percentage of votes for each candidate. These variables include:

@@

# Model {#sec-model}
The goal of our modeling strategy is twofold. Firstly, we aim to predict the percentage of votes each presidential candidate will receive using polling data from YouGov. Secondly, we seek to understand how key factors—such as political party, candidate name, sample size, and polling end date—affect vote share predictions.

@@

## Model set-up
Define $y_i$ as the predicted percentage of votes for candidate $i$, and $\texttt{party}_i$, $\texttt{candidate}_i$, $\texttt{sample\_size}_i$, and $\texttt{end\_date}_i$ as the political party, candidate name, sample size, and polling end date for candidate $i$ respectively.

@@

$$y_i | \mu_i, \sigma \sim \text{Normal}(\mu_i, \sigma)$$

@@

$$\mu_i = \alpha + \beta_1 \cdot \texttt{party}_i + \beta_2 \cdot \texttt{candidate}_i + \beta_3 \cdot \texttt{sample\_size}_i + \beta_4 \cdot \texttt{end\_date}_i$$

@@

$$\alpha \sim \text{Normal}(0, 2.5)$$
$$\beta_1, \beta_2, \beta_3, \beta_4 \sim \text{Normal}(0, 2.5)$$
$$\sigma \sim \text{Exponential}(1)$$

@@

## Model justification
We expect a significant relationship between the predictors and the percentage of votes. Specifically, political party is expected to have a substantial impact, as previous polls suggest that party affiliation strongly correlates with voter preferences. Additionally, sample size is an important predictor, as larger sample sizes tend to provide more reliable estimates. Polls conducted closer to the election (end date) may also capture more accurate voter sentiments, leading to better predictions.

@@

# Results {#sec-result}
Our results are summarized in @tbl-modelresults by using the modelsummary package [@modelsummary]. The model was designed to predict the percentage of votes each presidential candidate might receive based on several key factors: political party, candidate name, sample size, and polling end date. Below, we present a table of the model's coefficients, followed by visualizations of the relationship between the predictors and the predicted vote share.

@@

@@

modelsummary::modelsummary(
  list(
    "Vote Share Prediction Model" = first_model
  ),
  statistic = "mad",  # Mean absolute deviation
  fmt = 2  # Format to 2 decimal places
)%>%
  kableExtra::kable_styling(font_size = 8, full_width = TRUE)
```

@@

## Key Findings
- Political Party: The results show that the Republican party has a small positive effect on vote share predictions, while third-party candidates generally have lower predicted percentages.

@@

## Visualization of Results
We now turn to graphical representations to illustrate the relationship between sample size and predicted vote percentage, as well as the effect of political party on the predicted vote share.

@@

# Discussion {#sec-disscussion}
## Overview of Findings
In this paper, we built a predictive model to estimate the vote share of U.S. presidential candidates using polling data, with key predictors including political party, candidate name, sample size, and polling end date. The goal was to understand how these factors influence predicted vote shares, and to gain insights into the dynamics of political polling. The model’s high $R^2$ value (0.964) indicates it explains a substantial amount of variation in vote predictions, suggesting that it successfully captures relevant trends in the data. This outcome offers a deeper understanding of the factors driving poll-based vote share predictions in U.S. elections.

## Insights into Political Influence on Vote Share
One key finding from this analysis is the impact of political party on vote share predictions. Our model indicates that candidates from major parties, particularly Republicans, tend to receive higher predicted vote shares compared to third-party candidates. This is consistent with historical trends, where major-party candidates generally dominate U.S. elections. The model reinforces the idea that party affiliation is a powerful determinant in voter preferences, reflecting the established influence of major parties in American politics. This insight aligns with broader theories in political science, where party affiliation often serves as a shortcut for voters, helping them make quick decisions about candidates based on their general political orientation.

## Candidate-Specific Effects on Vote Share
Another important takeaway is the effect of candidate-specific factors on vote share predictions. Certain candidates, such as Joe Biden and Kamala Harris, show positive coefficients, indicating they are expected to receive a higher share of votes compared to others like Mike Pence or Vivek Ramaswamy. This suggests that individual characteristics and name recognition may play a role in influencing voter support. Recognizable figures with established reputations, such as former presidents or vice presidents, may have an advantage in polls due to higher visibility and public familiarity. This finding highlights the importance of candidate characteristics beyond party affiliation and points to the potential value of including more candidate-specific variables, such as favorability ratings, in future models.

## Limitations of Sample Size and Polling End Date as Predictors
Despite the high explanatory power of the model, certain predictors—particularly sample size and polling end date—show little to no effect on vote share predictions. This result might initially seem counterintuitive, as larger sample sizes are generally associated with higher reliability in survey research. However, in this case, the lack of impact could suggest that once a minimum sample threshold is met, the additional respondents do not significantly alter the predicted vote share. Similarly, the end date of the poll may have little impact because public opinion might not shift drastically over short periods, especially if polling occurs well before the election. This raises questions about the utility of these predictors in vote share models and suggests that additional contextual factors, such as the timing of major political events, could be more meaningful.

## Weaknesses and Next Steps
While this model provides valuable insights, it also has some limitations. First, the model does not incorporate a variable for state-level differences, which could be significant in the U.S. electoral system, where the Electoral College, not the popular vote, ultimately determines the election outcome. A more detailed model could include state as a predictor or even focus on state-level vote shares to estimate Electoral College outcomes.

@@

## Concluding Remarks and Future Directions
This analysis contributes to our understanding of how polling data can be used to predict election outcomes, highlighting the importance of political party and candidate characteristics in influencing vote shares. However, there remains much to explore. Future research could expand on this model by integrating additional predictors, such as candidate favorability and recent political events, or by building state-level models to predict Electoral College outcomes.

@@

# Appendix {-}
# Detailed Analysis of YouGov's Polling Methodology {#sec-appendix1}
## Overview of YouGov's Polling Approach
YouGov is a prominent polling agency known for its methodological rigor and unique approach to online surveys [@YouGov]. This appendix delves into YouGov's methodology, examining its sample selection, recruitment techniques, and the reliability and limitations inherent in its survey process.

## Population, Frame, and Sample
The population targeted by YouGov’s polls comprises U.S. adult citizens, providing a frame that includes diverse demographics such as age, gender, race, income level, and political affiliation [@YouGov]. The samples are drawn from an online panel of respondents who voluntarily participate in YouGov’s surveys [@YouGov]. By leveraging an extensive online panel, YouGov strives to capture a broad, representative slice of public opinion on various political issues, including presidential election intent, candidate favorability, and policy priorities.

## Sampling and Recruitment
YouGov employs a non-probability sampling approach, specifically targeting individuals within its online panel [@YouGov]. While this method allows YouGov to reach a large and diverse set of respondents quickly, it introduces certain limitations in terms of randomization and representativeness compared to traditional random sampling methods. To mitigate these issues, YouGov uses sophisticated weighting techniques to adjust for demographic discrepancies, ensuring that the sample more accurately reflects the broader U.S. population.

## Sampling Approach: Trade-offs
The online nature of YouGov’s panel sampling allows for rapid and frequent polling. However, it also comes with trade-offs, particularly concerning coverage bias, as individuals without internet access or those less inclined to participate in online activities may be underrepresented. Additionally, while weighting adjustments improve representativeness, they cannot entirely compensate for the self-selection bias inherent in voluntary panel participation. This trade-off is a key factor to consider when interpreting results, as online samples may sometimes diverge from outcomes in broader, random-sample-based polls.

## Non-response Handling
To address potential non-response bias, YouGov employs weighting adjustments based on demographic factors such as age, gender, education, and political affiliation [@YouGov]. By adjusting responses according to these factors, YouGov attempts to balance out any biases introduced by individuals who choose not to respond to specific questions or surveys entirely. This weighting process helps align the sample's characteristics with the intended population, although it does not completely eliminate non-response bias.

## Questionnaire Design
YouGov’s questionnaires are carefully crafted to gather specific insights into voters’ opinions on candidates, political parties, and policy issues. The questions are standardized to allow comparison over time, aiding trend analysis. However, the online format of the questionnaire could impact responses, as participants are aware they are not in a monitored, controlled setting. Despite this limitation, YouGov’s design ensures clarity and consistency, although some complex topics may benefit from further simplification to enhance understanding across diverse education levels.

## Strengths and Weaknesses
### Strengths
- Speed and Flexibility: The online sampling and recruitment model enables YouGov to conduct polls swiftly, which is particularly valuable in fast-moving political contexts.

@@

### Weaknesses
- Selection Bias: As participants self-select into the online panel, there is an inherent selection bias that even weighting cannot fully mitigate.

@@

# Idealized Methodology and Survey for Forecasting the U.S. Presidential Election {#sec-appendix2}
This appendix provides a detailed methodology for conducting an election forecasting survey with a $100,000 budget. The methodology focuses on achieving representativeness, accuracy, and data quality. The survey includes stratified sampling, multi-channel recruitment, data validation, and careful questionnaire design, implemented via Google Forms.

## Methodology Overview
This survey aims to forecast U.S. presidential election outcomes by capturing voting intentions and priorities across various demographic groups. With a $100,000 budget, we estimate reaching a sample size of approximately 5,000 respondents. This funding covers recruitment, incentives, and platform usage costs, ensuring a robust dataset that represents the U.S. voting population.

## Sampling Approach
Stratified Random Sampling will be employed, focusing on:

- Stratification Variables: Age, gender, race, income, education, and geography.

- Sample Size: With the $100K budget, the target sample size is approximately 5,000 respondents, based on cost estimates for recruitment, incentives, and platform usage.

- Random Selection: Participants will be randomly selected within each stratum to ensure demographic balance.

@@

## Recruitment Strategy
To reach a diverse population of respondents, the survey will use multi-channel recruitment, including:

- Social Media Advertising: Targeted ads on platforms such as Facebook, Twitter, and Instagram, directed toward U.S. users of various demographics.

- Email Outreach: Partnerships with organizations that can share the survey link with their networks.

- Incentives: Respondents will receive a small monetary incentive (e.g., $10 gift card) upon completing the survey, increasing participation rates while staying within budget.

@@

## Data Validation and Quality Control
To ensure data accuracy, several quality control measures will be in place:

- Screening Questions: Initial questions to confirm eligibility (e.g., age, U.S. citizenship).

- Attention Checks: Questions designed to ensure respondents are paying attention, helping filter out low-quality responses.

- Duplicate Responses: IP tracking and other technical measures to prevent duplicate submissions.

- Post-Survey Weighting: To correct for any imbalances in the sample, responses will be weighted based on demographic factors according to U.S. Census data, ensuring the final results better reflect the general population.

## Poll Aggregation and Reporting
This survey will be conducted in waves, with data collected at regular intervals leading up to the election. Results from each wave will be aggregated to provide a rolling average of voting intentions, smoothing out anomalies and highlighting trends. This approach will allow the survey to detect shifts in public opinion as the election approaches, providing a dynamic view of voter sentiment.

@@

## Survey Design
### Introductory Section
**Introduction**

Thank you for participating in our U.S. presidential election survey. Your responses will help us understand voting trends across the country. All responses are anonymous.

**Contact Information**

For questions, contact us at yz.chen@mail.utoronto.ca
